% =========================================================================
% RESUME SENSEI - SAMPLE LATEX RESUME (CLASSIC ORANGE & STYLIZED)
% =========================================================================
% Compile with: pdflatex
% =========================================================================

\documentclass[10pt,a4paper]{article}

% --- Standard Packages ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[empty]{fullpage}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{array}

% --- Font Settings ---
\renewcommand{\familydefault}{\sfdefault} 

% --- Color Palette (Classic Orange and Charcoal) ---
\definecolor{sectcol}{RGB}{255,150,0}     % Orange accent color for headers/bars
\definecolor{bgcol}{RGB}{110,110,110}     % Dark grey for header band and dates
\definecolor{softcol}{RGB}{225,225,225}   % Light grey for horizontal rules
\definecolor{textColor}{RGB}{43,43,43}     % Charcoal for body text

% --- Page Margins (Locked for full-width banner alignment) ---
\geometry{
    a4paper,
    left=1.5cm,
    right=1.5cm,
    top=1.75cm,
    bottom=1.5cm
}

% --- Hyperref Setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=sectcol,
    urlcolor=sectcol,
    pdftitle={Resume},
    pdfauthor={Your Name}
}

% --- Custom Page Layout ---
\urlstyle{same}
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0mm}

% --- Table Alignments ---
\newcolumntype{x}[1]{%
>{\raggedleft\hspace{0pt}}p{#1}}%

% --- Custom Layout Macros ---

% Strut for colorbox height padding
\newcommand{\mystrut}{\rule[-.3\baselineskip]{0pt}{\baselineskip}}

% Standard mathematical triangle arrow (replacing TikZ drawings)
\newcommand{\larrow}{$\blacktriangleright$\ }

% Section header with colored orange box and white text (matching Jan's design)
\newcommand{\cvsection}[1]{
    \vspace{8pt}
    \colorbox{sectcol}{\mystrut \makebox[1\linewidth][l]{
        \textcolor{white}{\ \larrow \textbf{#1}}
    }}\\
    \vspace{-4pt}
}

% Stretched tabular metadata entry
\newcommand{\metasection}[2]{
    \begin{tabular*}{1\textwidth}{p{2.4cm} p{11.6cm}}
        \textcolor{sectcol}{\larrow \textbf{#1}} & #2 \\[8pt]
    \end{tabular*}
}

% Stretched event block with left-aligned date and right-aligned company
\newcommand{\cvevent}[3]{
    \vspace{6pt}
    \begin{tabular*}{1\textwidth}{p{2.3cm} p{10.8cm} x{3.9cm}}
        \textcolor{bgcol}{#1} & \textbf{#2} & \vspace{2.5pt}\textcolor{sectcol}{#3}
    \end{tabular*}
    \vspace{-12pt}
    \textcolor{softcol}{\hrule}
    \vspace{4pt}
}

% --- Custom Lists Setup (Tight spacing) ---
\setlist[itemize]{leftmargin=0.15in, labelsep=5pt, parsep=0pt, topsep=1pt, itemsep=2pt}

% =========================================================================
% DOCUMENT BEGINS
% =========================================================================
\begin{document}
\color{textColor}

% === TITLE HEADLINE (Full-width grey background banner) ===
\vspace{-20.55pt}
\hspace{-0.25\linewidth}\colorbox{bgcol}{\makebox[1.5\linewidth][c]{
    \HUGE{\textcolor{white}{\textsc{[Your Name]}}} \textcolor{sectcol}{\rule[-1mm]{1mm}{0.9cm}} \HUGE{\textcolor{white}{\textsc{Resume}}}
}}
\vspace{12pt}

% === META SECTION (CONTACT INFO) ===
\metasection{Email:}{\href{mailto:your.email@example.com}{your.email@example.com}}
\metasection{Phone:}{[Phone Number]}
\metasection{Location:}{[City, State]}
\metasection{Links:}{\href{https://linkedin.com/in/yourusername}{linkedin.com/in/yourusername} $\cdot$ \href{https://github.com/yourusername}{github.com/yourusername}}

\vspace{4pt}

% === PROFESSIONAL SUMMARY ===
\cvsection{Summary}
Senior Software Engineer with 6+ years of experience specializing in backend architecture, database optimization, and cloud infrastructure. Proven track record of improving application latency by 40\% and developer velocity by automating release pipelines. Strong technical leader skilled in leading agile teams of 5--8 engineers to deliver secure, distributed systems.
\vspace{4pt}

% === TECHNICAL SKILLS ===
\cvsection{Skills}
\begin{tabular}{ @{} p{1.8in} @{} p{5.2in} }
    \textbf{Languages:} & Python, SQL (PostgreSQL, MySQL), JavaScript, TypeScript, Go, HTML5/CSS3 \\
    \textbf{Frameworks \& Libraries:} & React, Node.js, Express, Flask, Django, FastAPI \\
    \textbf{Cloud \& DevOps:} & AWS (S3, EC2, RDS, Lambda), Docker, Kubernetes, GitHub Actions, Jenkins \\
    \textbf{Databases:} & PostgreSQL, MySQL, Redis, MongoDB \\
    \textbf{Methodologies:} & Agile/Scrum, Software Development Life Cycle (SDLC), Test-Driven Development (TDD) \\
\end{tabular}
\vspace{4pt}

% === PROFESSIONAL EXPERIENCE ===
\cvsection{Experience}

\cvevent{August 2024 -- Present}{Senior Backend Engineer}{TechCorp}
\begin{itemize}
    \item Architected migration of 12 legacy Python microservices to AWS Lambda, resulting in 45\% infrastructure cost reduction and 99.99\% service availability.
    \item Spearheaded backend redesign of core checkout API, reducing average transaction response latency from 1.2s to 400ms (66\% improvement).
    \item Led team of 5 engineers to build real-time dashboard using React and WebSocket, boosting daily active user interaction by 30\%.
    \item Mentored 4 junior developers, introducing TDD practices that reduced production bug reports by 35\% within 6 months.
\end{itemize}
\vspace{6pt}

\cvevent{June 2021 -- July 2024}{Software Engineer}{Startup Inc}
\begin{itemize}
    \item Implemented indexing and query optimization across PostgreSQL databases, reducing dashboard loading times by 50\% (from 10s to 5s).
    \item Built automated CI/CD pipelines using GitHub Actions, decreasing weekly team manual release overhead from 8 hours to 15 minutes.
    \item Developed customer onboarding flows in React and Node.js, increasing account completion conversion rates by 22\%.
    \item Resolved 80+ critical system bug tickets during high-traffic Q4 sales season, maintaining 99.9\% application uptime.
\end{itemize}
\vspace{4pt}

% === PROJECTS ===
\cvsection{Key Projects}

\cvevent{Go, Redis, Docker}{Distributed Task Queue}{\href{https://github.com/yourusername}{github.com/yourusername}}
\begin{itemize}
    \item Designed an open-source task queue in Go capable of processing 10K+ concurrent background jobs.
    \item Utilized Redis for queue scheduling, achieving sub-millisecond task dispatch latency.
\end{itemize}
\vspace{6pt}

\cvevent{Python, AWS (S3/Lambda), React}{Serverless Analytics Tool}{Personal Project}
\begin{itemize}
    \item Created data aggregation tool that processed 1M+ daily server log events, visualizing metrics in a custom dashboard.
\end{itemize}
\vspace{4pt}

% === EDUCATION ===
\cvsection{Education}

\cvevent{Graduated 2021}{Bachelor of Science in Computer Science}{[University Name]}
\begin{itemize}
    \item GPA: 3.82/4.00 | Honors: Magna Cum Laude, Dean's List (6 semesters)
\end{itemize}
\vspace{4pt}

% === CERTIFICATIONS ===
\cvsection{Certifications \& Licenses}
\begin{itemize}[leftmargin=0.15in, labelsep=5pt, itemsep=1pt]
    \item AWS Certified Solutions Architect -- Associate (Amazon Web Services, 2025)
    \item Certified ScrumMaster (CSM) (Scrum Alliance, 2024)
\end{itemize}

% === ARTIFICIAL FOOTER (Full-width color band) ===
\null
\vspace*{\fill}
\hspace{-0.25\linewidth}\colorbox{bgcol}{\makebox[1.5\linewidth][c]{
    \mystrut \small \textcolor{white}{[Portfolio Link]} $\cdot$ \textcolor{white}{[GitHub Link]}
}}

\end{document}
